### 2016-07-08 errana.tex
First cut

We now define the two projection operators which are central to our error analysis. The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.

@@

the least upper bound projection of $J$ is defined as 

@@

where $J\in \R^n$. Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.

@@

The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:

@@

Further, define $\hg J$  as 

@@

(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,.

@@

In what follows we denote by $\hv$ the unique fixed point of $\hg$ i.e., $\hv = \hg \hv\,$. 

@@

Let $ r_1,  r_2,\ldots, r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$, respectively,

@@

We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$, and the rest of the arguments follow in the same manner as proof for \cref{srw}.

@@

||J^*-\hv||_{\mn}&\leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}&\nn\\+||\Gamma J^*-\hg J^*||_{\mn}\big).

@@

&||J^*-\hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+||\hg J^*-\hg \hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+\beta_\psi || J^*- \hv||_\mn,

@@

&\norm{J^*-\hv}_{\mn} \nn\\&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\

@@

For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.

@@

For  $r \in \R^k$ arbitrary vector, let $r'$ be

@@

||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn\\
&+||\Gamma J^*-\hg J^*||_{\mn}).

@@

\begin{align}\label{part}
&||\Phi r'-J^*||_{\mn}\nn\\&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.

@@

$r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. Then from \cref{srwalp} it follows that

@@

&||\hj-\hv||_{1,c}\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\

@@

&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).

@@

||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\nn\\

@@

&||J^*-\hj||_{1,c}\nn\\

@@

&||J_{\hu}-\hj||_{1,c}\nn\\&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\

@@

&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\

>>>>

We now define two projection operators which are central to our error analysis:
%The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.

@@

the \emph{ least upper bound projection} of $J$ is defined as 

@@

where $J\in \R^n$. 
Disregarding the constraint $r\in \N$, 
$\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.

@@

%The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
The definition of the second operator is as follows:

@@

Then, the \emph{approximate least upper bound (ALUB) projection operator}
$\hg \colon \R^n \ra \R^n$ is defined as 

@@

(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \R^n\,.

@@

In what follows we denote by $\hv$ the unique fixed point of $\hg$, i.e., $\hv = \hg \hv\,$. 

@@

For $i\in \{1,\dots,n\}$, $c=e_i$ let $r_i$ be a solution to the GRLP in \eqref{grlp}

@@

We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$.
The rest of the argument follows in the same manner as the proof for \cref{srw}.

@@

||J^*-\hv||_{\mn}
& \leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}
\nn\\
& {}\qquad \qquad+||\Gamma J^*-\hg J^*||_{\mn}\big).

@@

||J^*-\hv||_{\mn}
& \leq ||J^*-\hg J^*||_{\mn}+||\hg J^*-\hg \hv||_{\mn}\\
&\leq ||J^*-\hg J^*||_{\mn}+\beta_\psi || J^*- \hv||_{\mn},

@@

\norm{J^*-\hv}_{\mn} \nn
&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\

@@

For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$.

@@

For  $r \in \R^k$ arbitrary, let $r'$ be

@@

||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn
+||\Gamma J^*-\hg J^*||_{\mn}).

@@

||\Phi r'-J^*||_{\mn}\nn
&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma
	=\frac{2}{1-\beta_\psi}\gamma.
\label{part}

@@

Now, $r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. 
Then from \cref{srwalp} it follows that

@@

||\hj-\hv||_{1,c}
&\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\

@@

&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).\nn

@@

||J^*-\hj||_{1,c}
&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\\

@@

||J^*-\hj||_{1,c}\nn

@@

||J_{\hu}-\hj||_{1,c}\nn
&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\

@@

&\leq c^\top (I-\alpha P_{\hu})^{-1} \,\psi\, ||T\hj-\hj||_{\mn}\nn\\

### 2016-07-08 grlp.tex
First cut

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$. By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t.}\mb &\Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution.
In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by ntroducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$. By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t.}\mb &\Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution. \todoc{So what is our advice on how to select $\N$?}
In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.

### 2016-07-08 num.tex
First cut

In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates the quality of the constraint approximation. The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$. The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$. We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.

>>>>

In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates \todoc{right word?}
 the quality of the constraint approximation. The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$. The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$. We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.

### 2016-07-08 resdisc.tex
First cut

%!TEX root =  autocontgrlp.tex
\section{Discussion}
The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
\begin{enumerate}
\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
\item $||\Gamma J^*-\hg J^*||_{\mn}$.
\end{enumerate}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators. As a consequence, our result holds with probability $1$, unlike prior results on constraint sampling \cite{CS} that hold only with high probability. The error term $\etmn$ gives new insights into constraint selection. 
\begin{theorem}\label{st}
Let $s\in S$ be a state whose constraint was selected. Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align}
\end{theorem}
\begin{proof}
Let $r_{e_s,J^*}$ and ${r}'_{e_s,J^*}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$. However, since the constraints with respect to state $s$ have been sampled we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
\end{proof}
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Discussion}
The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors, namely
\begin{enumerate}
\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$, and
\item $||\Gamma J^*-\hg J^*||_{\mn}$.
\end{enumerate}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators and is completely deterministic, unlike prior results on constraint sampling \cite{CS} which are probabilistic.The error term $\etmn$ gives new insights into constraint selection:
\begin{theorem}\label{st}
Let $s\in S$ be a state whose constraint is selected in $W$. \todoc{Try to rephrase this..}
Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align}
\end{theorem}
\begin{proof}
Let $r_{e_s,J^*}$ and ${r}'_{e_s,J^*}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$. However, since the constraints with respect to state $s$ have been sampled we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
\end{proof}
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling \todoc{??} is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled. \todoc{??}
